Bayesian Insights into Aerial Bombing Strategies: An Ordered Logistic Regression Analysis of WWII Target Prioritization Against Germany

### 2024-04-18 paper/paper.qmd
polish the words, modify some styles

---
title: "Bayesian Insights into Aerial Bombing Strategies: An Ordered Logistic Regression Analysis of WWII Target Prioritization Against Germany"
author: 
  - Yunzhao Li
thanks: "Code and data are available at: https://github.com/yunzhaol/aerial_bomb_priority.git."
date: today
date-format: long
abstract: "During World War II, the strategic decisions about where and how the Allies bombed German industries played an essential role in the Allied campaign. This study employs Bayesian ordered logistic regression to methodically analyze how different factors—such as the industry type, the launching country, the bomb load, and the number of aircraft—shaped these decisions. Focusing on the preference for targeting essential oil refineries, the analysis sheds light on the calculated approach to disrupt Germany's war capabilities effectively. The insights from this research not only clarify the strategic rationale behind the Allies' bombing priorities but also enhance our understanding of their impact on the course of the war."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

The crux of this research lies in a detailed examination of a sampled subset of over 5,000 missions from extensive wartime records, representing a strategic selection designed to analyze the impact of various factors on target prioritization. These factors include the type of industry targeted, the leading country of the mission, the volume of bombs dropped, and the scale of aircraft involvement. Prior literature, such as studies by Grey [@Grey1999], has often provided broad overviews without delving into the interplay of these specific variables. By applying a Bayesian ordered logistic regression model, this study meticulously quantifies the influence of each factor, offering a clearer picture of the strategic considerations that shaped the Allied bombing strategy.

@@

The paper is organized to provide a clear and detailed examination of the strategic target prioritization during World War II aerial campaigns. Following the introduction in @sec-intro, @sec-data outlines the data employed in the study, describing the sources of historical military data, the variables selected for analysis, and the rationale behind these choices. @sec-model introduces the Bayesian ordered logistic regression model employed to analyze the relationships between our variables of interest, providing a statistical framework for understanding the strategic decisions behind target prioritization during World War II aerial campaigns. @sec-result presents the findings from the Bayesian ordered logistic regression model, detailing how different factors such as target industry and mission country influenced the prioritization of targets. @sec-discussion examines these results, discussing the strategic implications of the findings, the limitations of the current study, and suggesting avenues for future research to expand upon the insights gained. @sec-model-details shows plots for Posterior predictive check and Diagnostics and their analysis.

@@

This study aims to estimate the strategic priorities that guided the Allied forces in their aerial bombing campaigns against German industries during World War II. By analyzing various factors such as the type of industry targeted, the country leading the mission, the tonnage of bombs dropped, and the number of aircraft involved, this research seeks to understand how these variables influenced the decision-making processes regarding target selection. The core goal is to determine the causal effect of these factors on the prioritization of bombing targets, thereby shedding light on how strategic necessities, resource availability, and tactical choices shaped the wartime operations.

@@

- `**Target Industry (TGT_INDUSTRY)**`: Identified based on the strategic value, targeting industries critical to the war effort, such as oil refineries and transportation networks.
- `**Country of Mission (COUNTRY_FLYING_MISSION)**`: Considered to analyze differences in target prioritization across the Allied nations.
- `**Total Tons of Bombs (TOTAL_TONS)**`: Used to gauge the intensity and importance assigned to each mission.
- `**Aircraft Attack (AC_ATTACKING)**`: Reflected the scale of the mission and was indicative of the level of commitment to the target.

Variables such as THEATER, TGT_TYPE, and MSN_TYPE were not included due to the presence of extensive missing values or the complexity of their classifications, which could complicate the analysis. Similarly, variables like TOTAL_LBS, TIME_OVER_TARGET, AC_LOST, and AC_DAMAGED were omitted to keep the model focused and interpretable.

>>>>

---
title: "Bayesian Insights into Aerial Bombing Strategies: An Ordered Logistic Regression Analysis of WWII Target Prioritization Against Germany"
author: 
  - Yunzhao Li
thanks: "Code and data are available at: https://github.com/yunzhaol/aerial_bomb_priority.git."
date: today
date-format: long
abstract: "During World War II, the strategic decisions about where and how the Allies bombed German industries played an essential role in the Allied campaign. This study employs Bayesian ordered logistic regression to methodically analyze how different factors—such as the industry type, the launching country, the bomb load, and the number of aircraft—influenced the prioritization of targets. Focusing on the strategic choice to target essential oil refineries, the analysis highlights how these attacks were aimed to cripple Germany's war capabilities effectively. The insights from this research not only clarify the strategic rationale behind the Allies' bombing priorities but also enhance our understanding of their impact on the course of the war."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

The crux of this research lies in a detailed examination of a sampled subset of over 5,000 missions from extensive wartime records, representing a strategic selection designed to analyze the impact of various factors on target prioritization. These factors include the type of industry targeted, the leading country of the mission, the volume of bombs dropped, and the scale of aircraft involvement. Prior literature, such as studies by Grey [@Grey1999], has often provided broad overviews without delving into the interplay of these specific variables. By applying a Bayesian ordered logistic regression model, this study effectively quantifies the influence of each factor, offering a clearer picture of the strategic considerations that shaped the Allied bombing strategy.

@@

The paper is organized to provide a clear and detailed examination of the strategic target prioritization during World War II aerial campaigns. Following the introduction in @sec-intro, @sec-data outlines the data employed in the study, describing the sources of historical military data, the variables selected for analysis, and the rationale behind these choices. @sec-model introduces the Bayesian ordered logistic regression model employed to analyze the relationships between our variables of interest, providing a statistical framework for understanding the strategic decisions behind target prioritization during World War II aerial campaigns. @sec-result presents the findings from the Bayesian ordered logistic regression model, detailing how different factors such as target industry and mission country influenced the prioritization of targets. @sec-discussion examines these results, discussing the strategic implications of the findings, the limitations of the current study, and suggesting avenues for future research to expand upon the insights gained. @sec-model-details shows plots for Posterior predictive check and Diagnostics as well as their analysis.

@@

This study aims to estimate the strategic priorities that guided the Allied forces in their aerial bombing campaigns against German industries during World War II. By analyzing various factors such as the type of industry targeted, the country leading the mission, the tonnage of bombs dropped, and the number of aircraft involved, this research seeks to understand how these variables influenced the decision-making processes regarding target selection. The core goal is to determine the causal effect of these factors on the prioritization of bombing targets, thereby examining how strategic necessities, resource availability, and tactical choices shaped the wartime operations.

@@

- **Target Industry (`TGT_INDUSTRY`):** Identified based on the strategic value, targeting industries critical to the war effort, such as oil refineries and transportation networks.
- **Country of Mission (`COUNTRY_FLYING_MISSION`):** Considered to analyze differences in target prioritization across the Allied nations.
- **Total Tons of Bombs (`TOTAL_TONS`):** Used to gauge the intensity and importance assigned to each mission.
- **Aircraft Attack (`AC_ATTACKING`):** Reflected the scale of the mission and was indicative of the level of commitment to the target.

*THEATER*, *TGT_TYPE*, and *MSN_TYPE* were not included due to the presence of extensive missing values or the complexity of their classifications, which could complicate the analysis. Similarly, variables like *TOTAL_LBS*, *TIME_OVER_TARGET*, *AC_LOST*, and *AC_DAMAGED* were omitted to keep the model focused and interpretable.
